% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

\hypertarget{combinations}{%
\section{Combinations}\label{combinations}}

\hypertarget{counting-subsets}{%
\subsection{Counting Subsets}\label{counting-subsets}}

Our next problem is counting subsets of a given size chosen from a set
of a given size.

\textbf{Question:} How many different \(k\) element subsets does a set
with \(n\) elements have?

\vfill\eject

\hypertarget{theorem-on-counting-subsets}{%
\subsection{Theorem on counting
subsets}\label{theorem-on-counting-subsets}}

\textbf{Proposition:} The number of \(k\) element subsets of a set with
\(n\) elements is called \(\binom{n}{k}\). This number is read ``\(n\)
choose \(k\)'' and it is called a ``binomial coefficient''. The formula
for \(\binom{n}{k}\) is: \[
\binom{n}{k}=\frac{n!}{(n-k)!k!}
\]

\textbf{Proof:} First we give the book's proof.

\vfill\eject

\textbf{Proof:} now we give a proof by strong induction.

\vfill\eject

\hypertarget{examples}{%
\subsection{Examples}\label{examples}}

\textbf{Problem 2, page 89:} If a set has \(100\) elements, how many
subsets of \(A\) have \(5\) elements? How many have \(10\) elements? How
many have \(99\) elements?

\vfill\eject

\textbf{Problem 5, page 89:} How many \(16\) digit binary strings
contain exactly seven \(1\)'s?

\vfill\eject

\textbf{Problem 11, page 89:} How many positive 10 digit integers
contain no zeros and exactly three 6's?

\vfill\eject

\textbf{Problem 19, page 89:} A 5-card poker hand is called a
\emph{flush} if all cards are the same suit. How many different flushes
are there?

\end{document}
